### 2024-07-23 cognitive-bias.qmd
20240723 - draft and in-group bias

- overconfidence bias
- confirmation bias
- recency bias
- hindsight bias
- loss aversion bias
- endowment bias
- bandwagon effect bias
- Dunning–Kruger effect bias

@@

>>>>

- overconfidence bias
- confirmation bias
- in-group bias
- recency bias
- hindsight bias
- loss aversion bias
- endowment bias
- bandwagon effect bias
- Dunning–Kruger effect bias

@@

### In-Group Bias {#sec-cognitiveBiasesInGroup}

*In-group bias* is the tendency for people to prefer others who are members of their same (in-)group.
For instance, a manager whose favorite team is the Dallas Cowboys might try to draft mostly Cowboys players, regardless of their historical performance.

### 2024-07-23 draft.qmd
20240723 - draft and in-group bias

@@

An alternative to the "stars and scrubs" approach is to wait to draft more "high-value" players after other managers have over-paid for players.

>>>>

One factor that is *not* included above is whether a player is on your favorite team.
Managers commonly like to draft players on their favorite teams (e.g., Cowboys, Eagles).
That is fine—fantasy football is a game.
Do what is fun for you.
However, if your goal is to select the best players, leave your allegiances at the door.
Selecting players based on their playing for your favorite team—rather than based on performance—is a form of [cognitive bias](#sec-cognitiveBias).

@@

An alternative to the "stars and scrubs" approach is to wait to draft more "high-value" players after other managers have over-paid for players.
In any case, having some small amount of cap left over toward the end of the draft can help you draft good value players to fill out your bench spots for cheap (e.g., $2).
